### 2023-03-27 reachable-resilience.tex
up
Downward reachability reduction to reachable resilience

\problemx{Rachable-resilience problem for WSTS (RRP)}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $\Safe$ with a given basis, a decidable downward-closed set $\Bad$.}
{$ ~ \forall s' \in \Bad ~ (s \rightarrow^* s') \implies \exists s'' \in \Safe ~ s' \rightarrow^{*} s''$ ?\newline}

@@

\begin{proposition}\label{reductions}
Coverability and $t$-liveness are reduceable to the reachable resilience problem.
%	home state and reachability
\end{proposition}

@@

@@

\begin{proof}{Sketch}
Let us consider a LCS where erasing a message take one step. Then the upward compatibility is not strong. 
For instance with a rule $\delta(q,b) = \text{ add some }b $,
we have $(q,b) \to (q,bb)$, $(q, baaa) \geq (q,b)$ and
$(q, baaa) \to^* (q,bb)$ however it takes more than a single step.

>>>>

\problemx{Reachable-resilience problem for WSTS (RRP)}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $\Safe$ with a given basis, a decidable downward-closed set $\Bad$.}
{$ ~ \forall s' \in \Bad ~ (s \rightarrow^* s') \implies \exists s'' \in \Safe ~ s' \rightarrow^{*} s''$ ?\newline}

@@

\begin{proposition}\label{reductions}
Coverability and $t$-liveness are reducible to the reachable resilience problem.
%	home state and reachability
\end{proposition}

@@

\problemx{Downward reachability}
{A state $s$, a downward-closed set $D$.}
{$s \to^* D$? \newline}

\begin{theorem}
The downward reachability problem is reducible to the reachable resilience problem.
\end{theorem}

\begin{proof}
Take $\Safe = \emptyset$ and $\Bad = D$.
The reachable resilience problem then asks
whether $post^*(s) \cap D \subseteq \emptyset$.
If the answer is negative then $s \to^* D$,
else $s \not\to^* D$.
\end{proof}

@@

\begin{proof}[Sketch]
Let us consider a LCS where erasing a message take one step. Then the upward compatibility is not strong. 
For instance with a rule $\delta(q,b) = \text{ add some }b $,
we have $(q,b) \to (q,bb)$, $(q, baaa) \geq (q,b)$ and
$(q, baaa) \to^* (q,bb)$ however it takes more than a single step.
